+% Richard Boeri Decal's CV.
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Richard Decal <richard.decal-at-ncf.edu> http://www.ricardodecal.com
% credit to Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd for the grey boxes
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[a4paper,12pt]{article}
\renewcommand{\familydefault}{\sfdefault}
 
 % for math ops on widths e.x. \textwidth-1cm
\usepackage{calc}
 
%%%%%%%%%%%%
%style stuff
%%%%%%%%%%%%
%\newlength{\outerbordwidth}
\raggedbottom
%\raggedright

\usepackage{framed}
\usepackage{tocloft}
\usepackage{multicol} % for the multiple column'd list


%-----------------------------------------------------------


%make list unindented later
\usepackage{enumitem}

%compress the lines
\usepackage{setspace}
%\setstretch{0.9}
%\halfspacing

%page numbers and labels
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[margin=1in]{geometry}
\cfoot{\bfseries Decal CV \thepage} % except the center
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%Margin setup
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{0in}
%\setlength{\paperheight}{11in}
%\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
%\setlength{\textheight}{9.3in}
%\setlength{\textwidth}{7in}
\setlength{\topmargin}{0in}
\setlength{\topskip}{0in}
%\setlength{\voffset}{0.1in}
\setlength{\itemsep}{0pt}
\setlength{\marginparsep}{0pt}


% remove paragraph indents
\setlength{\parindent}{0pt}
%-----------------------------------------------------------
%Custom commands

% Grey header bars
% credit to Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
\usepackage[svgnames]{xcolor}
\definecolor{mygrey}{gray}{0.94}
\newcommand{\resheading}[1]{{\hspace{-9pt} \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textmd{~~\large \textbf{#1} \vphantom{p\^{E}}}}\end{minipage}}\vspace{6pt}} }

%\newcommand{\resheading}[1]{{\vspace*{.06in} \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textmd{\large \textbf{#1} \vphantom{p\^{E}}}}\end{minipage}}} }

%\newcommand{\resheading}[{1}]{     \vspace*{.06in} \colorbox{mygrey} {\begin{minipage} { \textwidth}{\textmd{ {\large #1} } \vphantom{p\^{E}} } \end{minipage}  } }

\newcommand{\ressubheading}[4]{{\begin{minipage}{\textwidth}
        \textbf{#1} \hfill #2 \\
        \textit{#3} \hfill #4 \\
        \end{minipage}}}

%\renewcommand*\descriptionlabel[1]{\hspace\labelsep\emph{#1 -}}


%-----------------------------------------------------------

        
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,    
    urlcolor=blue,
    breaklinks=true
}

\usepackage[hyphenbreaks]{breakurl}

% symbols
\usepackage{fontawesome}

% custom dates
\usepackage{datetime2}

% provides tabularx
\usepackage{ltablex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\Huge Richard Boeri Decal} \\
%Artificial Intelligence Engineer \\
{\small \faMapMarker~ Asheville, NC, USA $\cdot$ \faPhone~ (+1) 48-448-DECAL $\cdot$ \faEnvelope~ \href{mailto:richard.decal@gmail.com}{richard.decal@gmail.com}  \\ \faGithubAlt~ \href{https://github.com/crypdick}{crypdick} $\cdot$~\faStackOverflow~  \href{https://stackoverflow.com/users/4212158/crypdick}{crypdick} $\cdot$ ~\faLinkedin~ \href{https://www.linkedin.com/in/richarddecal/}{richarddecal}  $\cdot$ ~\faTwitter~ \href{https://twitter.com/AIjedi}{AIjedi}  $\cdot$ ~\faHome~  \href{http://www.ricardodecal.com}{ricardodecal.com}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Profile}

Machine learning scientist on a personal and professional mission to fight against climate change. Expertise in applying cloud computing and statistical modeling to engineering, scientific, and real-world problems. Work in team-contexts to create and modify scientific software libraries to process and understand noisy data generated by stochastic real-world processes. Able to seek input from outside experts to create domain-crossing solutions designed to scale. Former molecular biologist.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}

% recruited 
% Develop and implement 
% design, implementation, negotiation and execution 
% investors
% full lifecycle
% manage, work with
% Produce and manage
% Instrumental in the development of 
%  Involved in the strategy, planning, and execution of official company events in support of Employee Engagement.
% Provide action recommendations,  analysis, and strategies 
% Maintain confidentiality and legal policy in accordance with federal law, i
% Pipelines
% 
%    researching, consulting, analysing and evaluating system program needs
%    identifying technology limitations and deficiencies in existing systems and associated processes, procedures and methods
%    testing, debugging, diagnosing and correcting errors and faults in an applications programming language within established testing protocols, guidelines and quality standards to ensure programs and applications perform to specification
%    writing and maintaining program code to meet system requirements, system designs and technical specifications in accordance with quality accredited standards
% encoded
% roadmap
%    writing, updating and maintaining technical program, end user documentation and operational procedures
%    providing advice, guidance and expertise in developing proposals and strategies for software design activities such as financial evaluation and costings for recommending software purchases and upgrades
% spatial statistics
% 

\ressubheading{Lead Full-Stack Machine Learning Engineer}{Fully Remote}{Dendra Systems}{Feb. 2020 --- Now}

\vspace{-6pt} Developed and refined, in collaboration with institute stakeholders, a development plan for a machine learning group. Enabling whole-ecosystem restoration using deep learning.
\begin{itemize}
\item Architect, develop, maintain, and monitor infrastructure to facilitate the training, evaluation, and deployment of machine learning models.
	\begin{itemize}
	\item Responsible for full life-cycle of dataset and model artifact creation, quality assurance; tracking artifact lineage, parameters for reproducibility (\texttt{Kedro}).
	\item Scaled data processing workloads to terabyte-scale tabular and raster data (\texttt{Ray Distributed, Dask-ML, Modin}).
	\item Scaled ML workflows: hyperparameter tournaments, model training, and serving (\texttt{Ray[Tune, SGD, Serve, Autoscaler], EC2}).
	\item Created, optimized distributed queues, clients to maximize cluster I/O (\texttt{S3, Ray}).
    \item Enforced code quality and correctness using pre-commit hooks, automated CI (\texttt{Bitbucket Pipelines}), property-based testing (\texttt{Hypothesis}), run-time validation (\texttt{Pandera}), design-by-contract (\texttt{typeguard, icontracts}).
	\end{itemize}

\item Headed Research, experimentation, and development of novel classification systems.
    \begin{itemize}
      \item Researched, experimented, and productionized techniques for dealing with extremely imbalanced datasets, including: state-of-the-art data augmentation techniques, sampling strategies,  representation learning, domain-specific features (\texttt{skmulti-learn, imbalanced-learn}).
      \item Research semi-supervised methods to produce actionable insights in data-poor scenarios.
	  \item Examine and validate datasets; evaluate reliability of labelled data (\texttt{UMAP, Altair, streamlit}).
	  \item Translate business requirements into appropriate optimization functions.
	  \item Full-stack R\&D, full life-cycle ownership of custom ML models (\texttt{PyTorch}).
	  \item R\&D active learning methodology to improve data labeling efficiency.
    \end{itemize}
\item Produced screencasts to remotely present at company-wide Zoom meetings (\texttt{OBS Studio}).
\item Managed and mentored junior machine learning engineer with in-depth code reviews.
\item Roadmap, prioritize, and manage projects (\texttt{JIRA}).

\end{itemize}


\ressubheading{Lead Data Scientist}{Fully Remote}{PaceMate\textsuperscript{TM}}{Jan. 2019 --- Jan. 2020}

\vspace{-6pt} Build an end-to-end data processing and model training pipelines.

\begin{itemize}

\item  Automated remote detection of cardiac arryhtmias in Internet-enabled heart implants using deep learning.
    \begin{itemize}
	\item Developed processing pipelines for ECG data (\texttt{imbalanced-learn}, custom tools).
    	\item Working with cardiologists and software engineers to formulate business requirements (\texttt{YouTrack}).
    	\item Implemented state-of-the-art deep neural network for automated cardiac arrythmia classification specifically tuned for the device implanted in a majority of our patients (\texttt{Keras}).
    	\item Created data labelling dashboard for elecrophysiologists  to review model predictions (\texttt{Plotly Dash}).
    \end{itemize}
    
\item Created dashboard to collate, explore, and summarize key insights from our electronic medical records.
    \begin{itemize}
        \item Researched ML-assisted techniques for information extraction from extremely heterogeneous documents.
    \item Wrote and scaled performant ETL pipelines (\texttt{SQL, PySpark, spaCy}).
    \item Created dashboard to enable easy faceting and querying of EMR records to facilitate data-driven decision-making (\texttt{Plotly Dash}).
    \item Created report on our data inventory and trends in our data.
    \end{itemize}


\item Upheld SOC2 security standards with measures such as encryption at rest, traffic tunnelling, and instance hardening.
\item Presented my work and findings to various senior stakeholders such as CEO, CTO, and CIO. Interviewed by potential investors. Gave invited talk at local college.

\end{itemize}


\ressubheading{Data Scientist}{Sarasota, FL}{New College of FL, F.A.R. Institute}{Au. 2018 --- Dec. 2018}

\vspace{-6pt} Semester-long master's capstone project supervised by Dr. McDonald in partnership with the Florence A. Rothman Institute.


\begin{itemize}
\item Data-driven prediction of 30-day re-admission using visit clustering. 

\begin{itemize}
\item \texttt{visit2vec}: reduce high-dimensional patient visit data into low-dimensional embeddings using deep learning technique based on \texttt{word2vec} (\texttt{TensorFlow}).
\item Explored structure in patient visits data by clustering patient visits using t-SNE.
\end{itemize}



\item Modelled patient trajectories on years of heart failure patients from Sarasota Memorial Hospital.
\begin{itemize}
	\item Clustered patients over time based on cardiac and non-cardiac chronic conditions (\texttt{SQL, Pandas, PySpark}).
	\item Created network graphs characterizing interactions between multiple chronic conditions and heart failure and their effect on mortality (\texttt{NetworkX})
	\item Used finite state modeling to quantify interaction between chronic conditions and mortality (\texttt{PySpark, Numpy}).
\end{itemize}

\end{itemize}

\ressubheading{Research Intern}{Seatle, WA}{Peng Lab, Allen Institute for Brain Science}{June 2018 --- Aug. 2018}

\vspace{-6pt} Summer research project wherin I proposed a method that would automate the biggest bottleneck to high-throughput neural cell morphological analysis. 

\begin{itemize}
\item Deep reinforcement learning for tracing neural structures in petabytes of noisy fluorescent microscope data.

\begin{itemize}
\item Implemented proof-of-concept Deep Q Network using 3D convolutions to trace neural cell structures (\texttt{TensorFlow}).
\item Generated and augmented training data from manually traced microscopy dataset.
\item Created simulation environment for and engineered reward signals for training agents (\texttt{Matplotlib, OpenAI Gym}).
\item Contributor to \texttt{rl-medical}, a \texttt{tensorpack} extension for anatonmical landmark detection.
\end{itemize}

\end{itemize}

    \ressubheading{Classroom Mentor}{Fully Remote}{Udacity}{Dec. 2017 --- May 2018}
    
    Guided students 1-on-1 in Udacity's \textit{Intro to Programming Nanodegree}.
    \begin{itemize}
    \item Taught students how to use Python visualization libraries and Pandas DataFrames in the \textit{Python for Data Analysis Track}.
    \end{itemize}


\ressubheading{Research Assistant}{Seatle, WA}{Fairhall Lab, University of Washington}{Oct. 2014 --- Jan. 2016}

\vspace{-6pt} Developed agent-based dynamical models of mosquito thermal plume navigation behavior.

\begin{itemize}
\item Computed and visualized flight kinematic statistics and thermal sensing statistics using windtunnel flight data (\texttt{Numpy, Seaborn, scipy[interpolate, spatial, stats], sklearn, statsmodels}).
\item Formulated biophysical models of mosquito thermonavigation; applied numerical optimization algorithms to fit model to experimental data (\texttt{scipy[optimize], Pandas}).
\item Created animations of thermal plume navigation models (\texttt{Matplotlib 3D, MayaVi}).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Expertise}

\vspace{-1em}
\begin{tabularx}{\textwidth}{p{2.5cm}>{\arraybackslash}X}
    \bfseries{Specialties} & Deep Learning $\cdot$ Imbalanced datasets $\cdot$ Dimensionality reduction  $\cdot$ Computer vision $\cdot$  Effective visualization \\
    \bfseries{Languages} & Python $\cdot$ R Tidyverse $\cdot$ Bash $\cdot$  RegEx $\cdot$ Espa\~nol $\cdot$ English $\cdot$ Italiano \\
    \bfseries{Tools} & PyTorch, Keras, Tensorflow $\cdot$ (Geo)Pandas, \mbox{MongoDB}, PostgreSQL $\cdot$ Ray Distributed, PySpark, Dask $\cdot$ Plotly-Dash, Streamlit, Flask $\cdot$ Matplotlib, Seaborn, Altair, Plotly  $\cdot$ BeautifulSoup, Scrapy $\cdot$ Docker  \\
    \bfseries{MLOps} & AWS $\cdot$ Data Versioning $\cdot$ Kedro, MLFlow $\cdot$ Bitbucket CI Pipelines  \\
\end{tabularx}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}

\ressubheading{M.S. Data Science}{Sarasota, FL}{New College of Florida}{Aug. 2017 --- Dec. 2018}

%    \ressubheading{Artificial Intelligence Engineer Nanodegree}{}{Udacity}{Feb. 2017 --- May 2017}

%    \ressubheading{Research Fellowship}{Seattle, WA}{University of Washington}{Oct. 2014 --- Jan. 2016}

\ressubheading{B.A., Chemistry/Biology (with honors)}{Sarasota, FL}{New College of Florida}{Aug. 2007 --- May 2011}

\ressubheading{Early admission in lieu of 4th year high school}{Jupiter, FL}{Harriet L. Wilkes Honors College}{Sep. 2006 --- May 2007}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications, Presentations, \& Teaching}
\vspace{-19pt} \begin{itemize}
\item Invited talk on deep learning for automating caridac arrythmia at New College of Florida.
\item Published three peer-reviewed journal articles in high impact journals (\textit{Genetics}, \textit{PNAS}). Published an undergraduate honors thesis. 
\item Presented aforementioned research at three conferences (poster sessions).
\item Participated in several outreach programs for young students from low socioeconomic backgrounds. 
\item Invited talk on ML at high school STEM program in Torquinst, Argentina.
\end{itemize}

        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Selected Awards \& Grants}
     \ressubheading{NCF Data Scholar}{2017 ---  2018}{Full tuition waver for master's program.}{}
         
    \ressubheading{National Institutes of Health PA-12-149 Federal grant}{2014 --- 2016}{Fully covered my salary and expenses at the UW Dept of Biophysics.}{}

   
    \ressubheading{Florida ``Bright Futures" Scholar}{2007 --- 2011}{Merit-based scholarship, fully covered college tuition.}{}

    \ressubheading{Dubois-Felsmann Research Grant}{2010 --- 2011}{Covered reagent costs for my thesis experiments and conference admission     \& travel.}{}
    
\end{document}

