% Ricardo Boeri Decal's CV.
% (c) 2011 Ricardo Decal http://www.ricardodecal.com
% template inspirations from
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% credit to Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd for the grey boxes

% requirements on Ubuntu: texlive-full texlive-latex-extra texlive-fonts-extra

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.
\documentclass[a4paper,12pt]{article}

\renewcommand{\familydefault}{\sfdefault}

% for math ops on widths e.x. \textwidth-1cm
\usepackage{calc}

%%%%%%%%%%%%
%style stuff
%%%%%%%%%%%%
%\newlength{\outerbordwidth}
\raggedbottom  % no extra space at the bottom of the page
%\raggedright

\usepackage{framed}
\usepackage{tocloft}
\usepackage{multicol} % for the multiple column'd list


%-----------------------------------------------------------


%make list unindented later
\usepackage{enumitem}

%compress the lines
\usepackage{setspace}
%\setstretch{0.9}
%\halfspacing

%page numbers and labels
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[margin=1in]{geometry}
\cfoot{\bfseries Decal CV \thepage} % except the center
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%Margin setup
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{0in}
%\setlength{\paperheight}{11in}
%\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
%\setlength{\textheight}{9.3in}
%\setlength{\textwidth}{7in}
\setlength{\topmargin}{0in}
\setlength{\topskip}{0in}
%\setlength{\voffset}{0.1in}
\setlength{\itemsep}{0pt}
\setlength{\marginparsep}{0pt}


% remove paragraph indents
\setlength{\parindent}{0pt}
%-----------------------------------------------------------
%Custom commands

% Grey header bars
% credit to Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
\usepackage[svgnames]{xcolor}
\definecolor{mygrey}{gray}{0.94}
\newcommand{\resheading}[1]{{\hspace{-9pt} \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textmd{~~\large \textbf{#1} \vphantom{p\^{E}}}}\end{minipage}}\vspace{6pt}} }

%\newcommand{\resheading}[1]{{\vspace*{.06in} \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textmd{\large \textbf{#1} \vphantom{p\^{E}}}}\end{minipage}}} }

%\newcommand{\resheading}[{1}]{     \vspace*{.06in} \colorbox{mygrey} {\begin{minipage} { \textwidth}{\textmd{ {\large #1} } \vphantom{p\^{E}} } \end{minipage}  } }

\newcommand{\ressubheading}[4]{{\begin{minipage}{\textwidth}
                                    \textbf{#1} \hfill #2 \\
                                    \textit{#3} \hfill #4 \\
\end{minipage}}}

%\renewcommand*\descriptionlabel[1]{\hspace\labelsep\emph{#1 -}}


%-----------------------------------------------------------


\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    breaklinks=true
}

\usepackage[hyphenbreaks]{breakurl}

% symbols
\usepackage{fontawesome}

% custom dates
\usepackage{datetime2}

% provides tabularx
\usepackage{ltablex}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
    {\Huge Ricardo Boeri Decal}
        \\
%Artificial Intelligence Engineer \\
        {\small \faMapMarker~ San Francisco, CA, USA $\cdot$ \faPhone~ [redacted] $\cdot$ \faEnvelope~ \href{mailto:public@ricardodecal.com}{public@ricardodecal.com}  \\ \faGithubAlt~ \href{https://github.com/crypdick}{crypdick} $\cdot$~\faStackOverflow~  \href{https://stackoverflow.com/users/4212158/crypdick}{crypdick} $\cdot$ ~\faLinkedin~ \href{https://www.linkedin.com/in/rdecal/}{rdecal} $\cdot$ ~\faGraduationCap~ \href{https://scholar.google.com/citations?user=4ODJ78oAAAAJ}{GScholar} $\cdot$ ~\faHome~  \href{https://www.ricardodecal.com}{RicardoDecal.com}} 
    \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \resheading{Profile}

    Senior ML researcher with 10 years across research and industry, including molecular biology, computational neuroscience, and production ML. Track record owning end-to-end ML work: data engines for long-tailed open-world inference, distributed training infrastructure on Ray, and ML reliability under real-world distribution shift. Currently a Machine Learning Researcher at Latent Health, training AI models to modernize healthcare.\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \resheading{Expertise}
%
%    \vspace{-1em}
%    \begin{tabularx}{\textwidth}{p{2.5cm}>{\arraybackslash}X}
%        \bfseries{Specialties} & Deep Learning for Computer Vision $\cdot$ Imbalanced datasets $\cdot$ Dimensionality reduction  $\cdot$  Effective visualization                                                                                                                \\
%        \bfseries{Languages}   & Python $\cdot$ R Tidyverse $\cdot$ Bash $\cdot$  RegEx $\cdot$ Espa\~nol $\cdot$ English $\cdot$ Italiano                                                                                                                                         \\
%        \bfseries{Tools}       & PyTorch, Keras, Tensorflow $\cdot$ (Geo)Pandas, PostgreSQL $\cdot$ Ray/Anyscale, PySpark, Dask $\cdot$ Plotly-Dash, Streamlit, Flask, Gradio $\cdot$ Matplotlib, Seaborn, Altair, Plotly  $\cdot$ Pandera, Great Expectations $\cdot$ Docker \\
%        \bfseries{MLOps}       & AWS ecosystem $\cdot$ MetaFlow, Sagemaker, Kedro, MLFlow $\cdot$ Bitbucket CI/CD
%    \end{tabularx}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \resheading{Machine Learning Experience}
  
    \ressubheading{Machine Learning Researcher}{San Francisco, CA}{\href{https://www.latenthealth.com/}{Latent Health}}{Jun. 2026 --- Now}

    \vspace{-6pt} Training AI models to modernize healthcare.\\

    \ressubheading{Machine Learning Engineer}{San Francisco, CA}{\href{https://www.anyscale.com/}{Anyscale}}{Jan. 2025 --- Jun. 2026}

    \vspace{-6pt} Anyscale builds Ray, the open-source distributed compute framework underlying RL post-training, large-scale training, and inference at frontier labs.
    \begin{itemize}
    \item Conceived, pitched, and leading \textbf{Ray-bench}: a benchmark for evaluating LLM agents on distributed-systems code (framework translation, Ray code generation from spec, bug fixing, code optimization), paired with \textbf{RayGym}, a sandboxed multi-node execution harness for code-RL post-training. Strategic goal: drive Ray adoption among coding agents by giving model providers a verifiable-rewards benchmark to train on. Currently leading data generation: scraping, LLM-assisted synthesis with rejection sampling, AST-based Ray-API verification, and decontamination against pre-training corpora.
    \item Conceived, pitched, and designing a separate RL environment to train a Ray Core resource auto-calibration model.
    \item Engineered scalable distributed Ray implementations of: GRPO-based RL post-training for LLMs, LLM-as-judge data curation, 670B-parameter LLM serving, multimodal training, and agentic workflows.
    \item Early user and feedback partner for Ray LLM and Ray Direct Transport (RDMA-based tensor transfer for disaggregated inference/training); surfaced bugs and informed design.
    \item Built agentic systems for automated debugging and codebase-wide standards enforcement.
    \item Designed benchmarks comparing performance and cost across Ray OSS and RayTurbo.
    \end{itemize}
    
    \ressubheading{Lead Machine Learning Engineer}{Remote}{\href{dendra.io}{Dendra Systems}}{Feb. 2020 --- Jan. 2025}

    \vspace{-6pt} Founding ML lead. Built end-to-end ML systems for large-scale, long-tailed visual recognition across thousands of classes --- data engine, training infrastructure, evaluation, and serving. Domain: aerial imagery for ecosystem monitoring.
    \begin{itemize}
        \item \textbf{Data engine for long-tailed, open-world inference across thousands of target classes.}
        \begin{itemize}
            \item 60\% training-data reduction at no performance cost via a novelty-maximizing data-pruning method I developed (original research, unpublished); yielded pareto-optimal (exponential) scaling laws.
            \item Active learning to systematically harvest high-leverage training data, preventing model hallucinations on out-of-distribution inputs.
            \item Few-shot models paired with an active-learning data-harvesting UI to onboard new classes and domains in hours instead of months (\texttt{Gradio}).
            \item Unsupervised ``trip-wires'' for detecting model hallucinations in production; alerts routed to annotation prioritization workflow (\texttt{Jira}).
            \item Annotation QA/QC: systematically surfaced mislabeled and partially labeled samples to create a ``self-healing'' training dataset.
        \end{itemize}
        \item \textbf{Training and inference infrastructure (Ray-native, cloud-scale).}
        \begin{itemize}
            \item Distributed, scale-agnostic infrastructure for training, hyperparameter tuning, and inference (\texttt{Ray/Anyscale, AWS Batch}).
            \item 20$\times$ training-cost reduction via Bayesian hyperparameter tournaments with aggressive early stopping (\texttt{Ray Tune, HyperOpt, ASHA}).
            \item Profiled and optimized multi-GPU throughput (\texttt{Grafana}).
            \item End-to-end automation of training/inference pipelines (\texttt{custom orchestrator}); later re-implemented serverless for reliability and cost (\texttt{Step Functions, API Gateway, $\lambda$, EventBridge}).
            \item Researched, experimented, and productionized novel ML techniques: models, samplers, optimization functions, augmentations.
        \end{itemize}
        \item \textbf{MLOps and reliability.}
        \begin{itemize}
            \item Sanity checks for detecting silent failures during training; stratified validation across data slices.
            \item Debugged model failures using interpretability methods (GradCAM, transformer attention maps) and visualization of training dynamics.
            \item Full artifact lineage and reproducibility (\texttt{MetaFlow}).
            \item Observability across pipelines (\texttt{Cloudwatch, Slack bots, UMAP, Sentry}); weekly metric reviews to prevent customer-impacting incidents.
            \item 80$\times$ acceleration in insights delivery via model-in-the-loop annotation tooling.
        \end{itemize}
        \item \textbf{ML leadership.} Founding ML lead; drove transformation from services to ML-product company. Owned ML roadmap, KPIs, and OKRs aligned with product and operations. ML automation increased throughput and profitability and unlocked new markets. Oversaw data-collection team and ran internal ``ML University'' lectures.
    \end{itemize}


    \ressubheading{Lead Data Scientist}{Remote}{\href{https://pacemate.com/}{PaceMate}}{Jan. 2019 --- Dec. 2019}

    \vspace{-6pt} \textit{PaceMate monitors transmissions from bluetooth-enabled heart implants, identifying life-threatening arrhythmias and alerting emergency services}. Solo ML hire; took cardiac arrhythmia detection from zero to deployed deep-learning system in a regulated, life-critical pipeline --- end-to-end ownership across data, modeling, clinician tooling, and SOC2 security.
    \begin{itemize}
        \item Trained SOTA deep neural network for arrhythmia classification, tuned to the implant device used by the majority of patients (\texttt{Keras}).
        \item Built ECG data-processing pipelines for highly imbalanced clinical data (\texttt{imbalanced-learn}, custom tools).
        \item Built clinician-facing labeling and prediction-review dashboard for electrophysiologists (\texttt{Plotly Dash}).
        \item Built EMR analytics dashboard with performant ETL across heterogeneous medical records to enable data-driven decision-making (\texttt{SQL, PySpark, spaCy, Plotly Dash}).
        \item Translated clinical requirements into ML specs with cardiologists; presented to C-suite and met with investors.
    \end{itemize}


    \ressubheading{Data Scientist}{Sarasota, FL}{New College of FL, \href{farinstitute.org}{F.A.R. Institute}}{Aug. 2018 --- Dec. 2018}

    \vspace{-6pt} Master's capstone (unpaid). Predicted 30-day hospital readmission via patient-visit embeddings (\texttt{visit2vec}, t-SNE); modeled chronic-condition trajectories of heart-failure patients with clustering, network graphs, and finite-state models (\texttt{SQL, PySpark, NetworkX, TensorFlow}).\\

%   [archived original capstone bullets, pre-rewrite]
%   \textit{The Florence A. Rothman Institute supports innovation in medical data analysis}. Semester-long master's capstone project supervised by Dr. Pat McDonald. Unpaid.
%   \item Data-driven prediction of 30-day readmission using visit clustering.
%       \item \texttt{visit2vec}: reduce high-dimensional patient visit data into low-dimensional embeddings using a technique inspired by \texttt{word2vec} (\texttt{TensorFlow}).
%       \item Explored structure in patient visits data by clustering patient visits using t-SNE.
%   \item Modeled patient trajectories on years of heart failure patients from Sarasota Memorial Hospital.
%       \item Clustered patients over time based on cardiac and non-cardiac chronic conditions (\texttt{SQL, Pandas, PySpark}).
%       \item Created network graphs characterizing interactions between multiple chronic conditions and heart failure and their effect on mortality (\texttt{NetworkX}).
%       \item Used finite state modeling to quantify interaction between chronic conditions and mortality (\texttt{PySpark, Numpy}).

    \ressubheading{Research Intern}{Seattle, WA}{Peng Lab, \href{alleninstitute.org}{Allen Institute for Brain Science}}{June 2018 --- Aug. 2018}

    \vspace{-6pt} Built a 3D Deep Q-Network for tracing neural structures in petabyte-scale fluorescent microscopy; designed the simulation environment and reward system end-to-end based on \href{https://www.nature.com/articles/s41467-019-11443-y}{manually traced microscope images} (\texttt{TensorFlow, rl-medical, OpenAI Gym}; \href{https://www.ricardodecal.com/projects/profundo-an-rl-agent-for-neural-cell-tracing/}{\textit{Profundo} writeup}).\\

%   [archived original Allen bullets, pre-rewrite]
%   \textit{The neuromorphology lab investigates the architecture of the brain at the population and single-cell level}. Proposed a method that would automate the biggest bottleneck to high-throughput neural cell morphological analysis.
%   \item Deep reinforcement learning for tracing neural structures in petabytes of noisy fluorescent microscope data.
%       \item Implemented proof-of-concept Deep Q Network using 3D convolutions to trace neural cell structures (\texttt{TensorFlow, rl-medical}).
%       \item Created simulation environment and reward system for training agents (\texttt{Matplotlib, OpenAI Gym}) based on manually traced microscope images.

    % \ressubheading{Classroom Mentor}{Remote}{\href{udacity.com}{Udacity}}{Dec. 2017 --- May 2018}

    % Provided 1-on-1 tutoring and code reviews for the \textit{Intro to Programming Nanodegree: Python for Data Analysis Track}.\\

    \ressubheading{Research Assistant}{Seattle, WA}{\href{https://compneuro.washington.edu/}{Fairhall Lab, University of Washington}}{Oct. 2014 --- Jan. 2016}

    \vspace{-6pt} Computational neuroscience lab. Self-funded via NIH PA-12-149 federal grant.
    \begin{itemize}
        \item Parameter inference: fit biophysical models of mosquito thermonavigation to wind-tunnel behavioral data via numerical optimization (\texttt{scipy.optimize, sklearn, statsmodels}).
        \item Wrote vectorized \texttt{numpy} routines for high-throughput processing of behavioral video data; computed kinematic and thermal-sensing statistics across the dataset.
    \end{itemize}

%   [archived original Fairhall bullets, pre-rewrite]
%   \textit{Computational neuroscience lab investigating the biophysics of neural cells}. I developed agent-based dynamical models of mosquito thermal plume navigation behavior.
%   \item Computed and visualized flight kinematic statistics and thermal sensing statistics using windtunnel flight data (\texttt{Numpy, Seaborn, scipy[interpolate, spatial, stats], sklearn, statsmodels}).
%   \item Formulated biophysical models of mosquito thermonavigation: applied numerical optimization algorithms to fit model to experimental data (\texttt{scipy[optimize], Pandas}).
%   \item Created animations of thermal plume navigation models (\texttt{Matplotlib 3D, MayaVi}).

    \ressubheading{Molecular Biologist}{Various}{Various}{Pre-2014}

    \vspace{-6pt} Before transitioning to AI/ML, I was a molecular biology researcher. Co-authored peer-reviewed work on Parkinson's disease (mitochondrial dysfunction in dopaminergic neurons; \textit{PNAS} 2012) and Wnt signaling (\textit{Genetics} 2012). Honors thesis on RNA interference mechanisms in \textit{C. elegans}.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \resheading{Education}

    \ressubheading{M.S. Data Science}{Sarasota, FL}{New College of Florida}{Aug. 2017 --- Dec. 2018}

%    \ressubheading{Artificial Intelligence Engineer Nanodegree}{}{Udacity}{Feb. 2017 --- May 2017}

    \ressubheading{B.A., Chemistry/Biology (with honors)}{Sarasota, FL}{New College of Florida}{Aug. 2007 --- May 2011}

    \ressubheading{Early admission (admitted 16 yrs old)}{Jupiter, FL}{Harriet L. Wilkes Honors College}{Jul. 2006 --- May 2007}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \resheading{Publications, Presentations, \& Teaching}

    * 2025 \textit{\href{https://www.anyscale.com/blog/deepseek-vllm-ray-google-kubernetes}{Deploy DeepSeek-R1 with vLLM and Ray Serve on Kubernetes}} --- end-to-end deployment guide for distributed serving of a 670B-parameter reasoning model.

    * 2025 \textit{\href{https://www.anyscale.com/blog/ray-direct-transport-rdma-support-in-ray-core}{Ray Direct Transport: RDMA Support in Ray Core}} --- technical write-up on RDMA-based tensor transfer for disaggregated inference/training.

    * ongoing \href{https://www.ricardodecal.com}{Personal blog} (80+ technical notes on Ray, LLMs, RL, ML internals, OSS projects). Selected: \textit{\href{https://www.ricardodecal.com/projects/self-authoring-llm-knowledge-base/}{Self-authoring LLM knowledge base}}, \textit{\href{https://www.ricardodecal.com/guides/using-ds-py-with-ray-data/}{Using DSPy with Ray Data}}, \textit{\href{https://www.ricardodecal.com/projects/slouchless-using-ai-to-improve-my-posture/}{Slouchless: VLM for posture correction}}.

    * 2025 Speaker at Ray meetups: \href{https://luma.com/u5p41kte}{Daft+Ray}, vLLM+Ray, Skypilot+Ray.

    * 2024 Talk at \textit{AI In Production Conference} on \href{https://www.aiinproduction.com/speakers/richard_decal}{data curation}.

    * 2021 Invited talk at \textit{Ray Summit}: \href{https://www.anyscale.com/events/2021/06/22/how-ray-and-anyscale-make-it-easy-to-do-massive-scale-ml-on-aerial-imagery}{\textit{How Ray and Anyscale Make it Easy to do Massive-scale ML on Aerial Imagery}} (\href{https://www.anyscale.com/blog/how-ray-and-anyscale-make-it-easy-to-do-massive-scale-machine-learning-on}{accompanying blog}).

    * 2019 Seminar at \textit{New College of FL}: \textit{Remote Sensing of Cardiac Arrhythmia at Scale using Deep Learning}.

    * 2019 Seminar at \textit{Escuela Secundaria Tecnica de Torquinst}: \textit{Intelligencia Artificial}.

%   * 2018 Classroom mentor for \textit{Udacity's Intro to Programming Nanodegree: Python for Data Analysis Track} (1-on-1 tutoring, code reviews).

    * 2015 UW Outreach: various educational events for students from low socioeconomic backgrounds.

    * 2012 \href{https://scholar.google.co.nz/citations?user=4ODJ78oAAAAJ&hl=en}{Two peer-reviewed journal articles} in \textit{Genetics} and \textit{PNAS}, also presented as posters at three national conferences.

    * 2007 Undergraduate honors thesis on RNA interference mechanisms in \textit{C. elegans}.\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   [archived awards section, pre-rewrite. NIH grant folded into Fairhall entry.]
%   \resheading{Selected Awards \& Grants}
%   \ressubheading{National Institutes of Health PA-12-149 Federal grant}{2014 --- 2016}{Self-funded grant covering salary and expenses at the UW Dept.\ of Biophysics.}{}
%   \ressubheading{NCF Data Scholar}{2017 --- 2018}{Full tuition waiver for master's program.}{}
%   \ressubheading{Florida ``Bright Futures'' Scholar}{2007 --- 2011}{Merit-based scholarship. Full undergraduate tuition.}{}
%   \ressubheading{Dubois-Felsmann Research Grant}{2010 --- 2011}{Covered reagent costs for my thesis experiments \& conferences.}{}

\end{document}
