% Richard Boeri Decal's CV.
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Richard Decal <richard.decal-at-ncf.edu> http://flavors.me/richarddecal
% credit to Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd for the grey boxes
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
 \renewcommand{\familydefault}{\sfdefault}
 
%%%%%%%%%%%%
%style stuff
%%%%%%%%%%%%
\usepackage[svgnames]{xcolor}
\definecolor{mygrey}{gray}{0.94}

%\newlength{\outerbordwidth}
\raggedbottom
%\raggedright

\usepackage{framed}
\usepackage{tocloft}
\usepackage{multicol} % for the multiple column'd list


%-----------------------------------------------------------
%Margin setup

%\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.3in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
%\setlength{\voffset}{0.1in}
\setlength{\parindent}{0in}
\setlength{\itemsep}{0pt}

%make list unindented later
\usepackage{enumitem}

%compress the lines
\usepackage{setspace}
%\setstretch{0.9}
%\halfspacing

%page numbers and labels
\usepackage{fancyhdr}
\pagestyle{fancy}
\cfoot{\bfseries \thepage} % except the center
\rfoot{Decal CV}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-----------------------------------------------------------
%Custom commands

%fancy headings

\newcommand{\resheading}[1]{{\vspace*{.06in} \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textmd{\large \textbf{#1} \vphantom{p\^{E}}}}\end{minipage}}} }


%\newcommand{\resheading}[{1}]{     \vspace*{.06in} \colorbox{mygrey} {\begin{minipage} { \textwidth}{\textmd{ {\large #1} } \vphantom{p\^{E}} } \end{minipage}  } }

\newcommand{\ressubheading}[4]{
        \textbf{#1} \hfill #2\\
        \textit{#3} \hfill #4 \\}

\renewcommand*\descriptionlabel[1]{\hspace\labelsep\emph{#1 -}}

% symbols like \Telefon, \Mobilefone, \Letter and \Email
\RequirePackage{marvosym}
% symbols used
\providecommand*{\listitemsymbol}{\Neutral}%{{\fontencoding{U}\fontfamily{ding}\selectfont\tiny\symbol{'102}}}
\providecommand*{\addresssymbol}{}
\providecommand*{\mobilesymbol}{\Mobilefone}
\providecommand*{\phonesymbol}{\Telefon}
\providecommand*{\faxsymbol}{\FAX}
\providecommand*{\emailsymbol}{\Letter}
\providecommand*{\homepagesymbol}{{\Large\ComputerMouse}}
%-----------------------------------------------------------

        
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,    
    urlcolor=blue
}
    \usepackage[hyphenbreaks]{breakurl}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Richard Boeri Decal} & \emailsymbol  \href{mailto:decal@uw.edu}{decal@uw.edu} \\
\textit{updated \today} & \homepagesymbol \href{https://github.com/isomerase/}{ Github.com/isomerase/}  \\

 
\end{tabular*}
\\
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}

    \ressubheading{University of Washington}{Seattle, WA}{Post-baccalaureate researcher.}{Jan. 2015 $\rightarrow$ Now}
 
    \ressubheading{New College of Florida}{Sarasota, FL}{B.A., Chemistry/Biology (Honors)}{Aug. 2007 $\rightarrow$ May 2011}
    Thesis: ``Ebbs and Glows: Quantifying Small RNA Concentrations in \textit{C. elegans}''\\

    \ressubheading{Harriet L. Wilkes Honors College}{Jupiter, FL}{Early admission in lieu of a high school senior year}{Sep. 2006 $\rightarrow$ May 2007}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic Projects \& Employment}


\ressubheading{\hypertarget{Mosquitogrant}Multisensory Integration in Mosquitos}{Seatle, WA}{University of Washington}{Nov. 2014 $\rightarrow$ Now}
Researcher in Dr.\ Adrienne Fairhall's lab. Our group is investigating multi-modal sensory integration and decision-making in mosquitos during turbulent odor and thermal plume tracking. We use electrophysiological \& tethered and untethered flight data to create models of decision making.\\

 \ressubheading{\hypertarget{whalevolunteering}Humpback Whale Census}{James Price Point, Australia}{Kimberley Community Whale Research Project}{Aug. 2012 $\rightarrow$ Oct. 2012}
    This research was a community-initiated peer-review at the proposed site of the world's second-largest liquefied gas processing plant and port. The oil conglomerate's study claimed few humpback whales migrated past James Price Point. Our \href{http://tinyurl.com/JPP-humpback-whale-survey-2013}{peer-review}'s estimates of the humpback population were an order of magnitude larger, a gross discrepancy.  \\

    \ressubheading{Honors Thesis and Baccalaureate Defense}{Sarasota, FL}{New College of Florida}{Aug. 2010 $\rightarrow$ May 2011}
   A capstone research project conducted in Dr.\ Katherine Walstrom's lab.  My \hyperlink{thesispub}{thesis} proposes a model for RNA Helicase A function in endogenous \emph{C. elegans} RNAi pathways. My baccalaureate exam was administered by a committee of faculty and consisted of a thesis defense followed by a comprehensive oral exam covering all courses I took at New College.\\

    \ressubheading{Tutorials}{Sarasota, FL}{New College of Florida}{Aug. 2007 $\rightarrow$ May 2011}
    I created classes using New College's tutorial system, in which students are able to design courses in collaboration with faculty. Highlights: ``Wikipedia: Community, Technology, Society", ``Quantitative RT-PCR", ``Arduino Programming", ``Invasive Species", and ``Organic Lab Research".\\

    \ressubheading{Genomics Outreach for Minorities Project (NSF-REU)}{Seattle, WA}{University of Washington}{May 2010 $\rightarrow$ Aug. 2010}
    A 12-week project conducted in Dr.\ Leo Pallanck's lab. I helped establish a method to grow, stain, and image primary dopaminergic neural culture from \textit{Drosophila} embryos in order to test whether Parkin and PINK1, proteins involved in Parkinson's disease, are recruited to depolarized mitochondria in dopaminergic neurons. This research was \hyperlink{neuronpub}{published} in \textit{PNAS}.\\

    \ressubheading{Lab Technician}{Sarasota, FL}{New College of Florida Dept. of Natural Sciences}{Feb. 2010 $\rightarrow$ Sep. 2010}
    Routine duties for the department, including autoclaving and disposing lab waste, preparing and sterilized solutions and agar plates, and preparing lab courses as needed. \\

    \ressubheading{Organic Lab Research Tutorial}{Sarasota, FL}{New College of Florida}{Sep. 2008 $\rightarrow$ Nov. 2009}
    A continuation of New College graduate Dan Kaplan's thesis research conducted in Dr.\ Paul Scudder's lab. I partially synthesized precursors to a novel high-valent iron-stabilizing macrocycle based on the active site of cytochrome P450.\\% My work was summarized in a paper entitled, ``Towards Synthesis of a Cytochrome P450 Mimic".\\

    \ressubheading{Summer Undergraduate Research Program (NSF-REU)}{Pittsburgh, PA}{Carnegie Mellon University}{May 2009 $\rightarrow$ Aug. 2009}
    A 10-week project conducted in Dr.\ Brooke McCartney's lab. I determined that APC2, a protein with probable roles in colon cancer tumorogenesis, did not interact with $\beta$-catenin of the Wnt pathway's destruction complex. I determined that a conserved APC2's N-terminal domain was not essential for its proper localization. This research was \hyperlink{carnegiepub}{published} in \textit{Genetics}.\\
    
    \ressubheading{Independent Study Project}{Sarasota, FL}{New College of Florida}{Jan. 2009}
    A 4-week project conducted under the direction of Dr.\ Necmettin Yildirim. Using MATLAB, we modelled biological and chemical systems, particularly oscillating kinetic systems such as the Brusselator.\\ % I presented my work in a seminar entitled, ``Modelling the Dynamics of Life".\\

    \ressubheading{Independent Study Project}{Sarasota, FL}{New College of Florida}{Jan. 2008}
    A 4-week project under the sponsorship of Dr.\ Elzie McCord. I reviewed chromatographic theory and learned how to operate gas and high-pressure liquid chromatographs. I researched and isolated triclosan, a ubiquitous bactericide and suspect carcinogen.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}

    %\textbf{Academic}
    
     \hypertarget{neuronpub} Burman JL, Yu S, Poole AC, \textbf{Decal RB} and Pallanck LJ. ``\href{http://www.pnas.org/content/early/2012/06/12/1120688109}{Analysis of neural subtypes reveals selective mitochondrial dysfunction in dopaminergic neurons from parkin mutants}". \textit{Proc Natl Acad Sci USA.} 2012 Jun 26;109(26):10438-43. \\            
    
      \hypertarget{carnegiepub} Kunttas-Tatli E, Zhou M, Zimmerman S, Molinar O, Zhouzheng F, Carter K, Kapur M, Cheatle A, \textbf{Decal R}, McCartney BM. ``\href{http://www.genetics.org/content/190/3/1059.full}{Destruction Complex Function in the Wnt Signaling Pathway of Drosophila Requires Multiple Interactions Between Adenomatous Polyposis Coli 2 and Armadillo}". \textit{Genetics}. 2012 Mar; 190(3):1059-75.\\    
    
       \hypertarget{thesispub} \textbf{\textbf{Decal RB}}. ``\href{http://tinyurl.com/RichardDecal-NCF-Thesis}{Ebbs and Glows: Quantifying Small RNA Concentrations in \textit{C. elegans}}". Honors thesis, New College of Florida. May 2011. 108 pages.\\
       
        
    
    %\textbf{Selected Blog Entries}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}

    
%(Accepted and Forthcoming)
    \textbf{Decal RB}, Burman JB, Pallanck L. ``Is Parkin Recruited to Damaged Mitochondria in Dopaminergic Neurons?" Society for Advancement of Chicanos and Native Americans in Science.  Anaheim, CA. September 2010. Poster.\\

    \textbf{Decal RB}, McCartney BM. ``APC2 Does Not Interact with in the $\beta$-Catenin Destruction Complex". Annual Sigma Xi Conference. The Woodlands, TX. November 2009. Poster.\\

    \textbf{Decal RB}, McCartney BM. ``APC2 Does Not Interact with in the $\beta$-Catenin Destruction Complex". Annual Biomedical Research Conference for Minorities. Phoenix, AZ. November 2009. Poster.\\
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching}


    \ressubheading{Upward Bound}{Seattle, WA}{University of Washington}{July 2010}
    Outreach program to educate high school students with low socioeconomic status. I presented a lecture on genetics and Parkinson's disease and performed hands-on demonstrations.\\        
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}


    \textsc{Computation}
        \begin{description}\setlength{\itemsep}{0mm}
        \item[Operating Systems] Proficient: MS Windows, Mac OS X, iOS, Linux, and Android.
        \item[Software] Proficient: office suites, image manipulation and analysis software, and other common productivity packages. Novice: PyMol.
        \item[Programming] Fluent: \LaTeX. Proficient: Python.
        \end{description}

     \textsc{Biology}\vspace*{-15pt}
        \begin{multicols}{2} \begin{itemize}[leftmargin=0.4cm]
        \item Standard biochemical and molecular biology assays
        \item \textit{C. elegans}, \textit{D. melanogaster}, \textit{E. coli}, and primary neural culture models
        \item UV-Vis, FT-IR, NMR, and mass spectroscopy
        \item Protein, RNA, DNA, and organelle purification
        \item Tissue fixation, immunohistochemistry, and LR White embedding
        \item Exclusion, ion exchange, affinity, gas, thin-layer, and high-pressure liquid chromatography
        \item Confocal, fluorescence, light, and phase contrast microscopy
        \item PCR, RT-qPCR, shotgun and Sanger sequencing, and BLAST
        \item Marine field collecting
        \item Organic synthesis
        \end{itemize}
        \end{multicols}
        
    \textsc{Personal}
        \begin{description}\setlength{\itemsep}{0mm}
        \item[Photography] I am a DSLR photographer and know how to use the Adobe suite (\href{https://www.flickr.com/photos/richarddecal/sets/72157640025469005/}{portfolio}).
        \item[Other] Fluent in English and Spanish. Known to dabble in the kitchen. I've played violin, piano, contrabass, and ukulele. Licensed scuba diver.
        \end{description}

        
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards, Grants \& Honors}

    \ressubheading{Florida ``First Generation" Scholar {\normalfont(two-time recipient)}}{}{New College of Florida}{Aug. 2009 $\rightarrow$ May 2011}
    Scholarship for minority students who are the first of their family to pursue higher education.\\ %TODO NIH


    \ressubheading{Florida ``First Generation" Scholar {\normalfont(two-time recipient)}}{}{New College of Florida}{Aug. 2009 $\rightarrow$ May 2011}
    Scholarship for minority students who are the first of their family to pursue higher education.\\

    \ressubheading{Florida ``Bright Futures" Scholar}{}{New College of Florida}{Aug. 2007 $\rightarrow$ May 2011}
    Florida's merit-based scholarship based on high school performance. Awarded full college tuition. \\

    \ressubheading{Four Winds Silver Scholar}{}{New College of Florida}{Aug. 2007 $\rightarrow$ May 2011}\
    Merit-based scholarship.\\
    
  \ressubheading{Student Recognition Award {\normalfont(two-time recipient)} }{}{New College of Florida} {Apr. 2011}\
    
    \ressubheading{Student Research Grant}{}{Dubois-Felsmann Research Endowment}{Nov. 2010}\
    Grant for honors thesis research. \$400.\\
    
    \ressubheading{Student Travel Grant}{}{Dubois-Felsmann Research Endowment}{Sep. 2009}\
    Grant to present my REU research. \$400.\\
    
    \ressubheading{ABRCMS Travel Award}{}{American Society for Microbiology}{Aug. 2009}\
    Grant to present my REU research. \$800.\\
    
    \ressubheading{Honors Scholarship}{}{Harriet L. Wilkes Honors College}{Sep. 2006 $\rightarrow$ May 2007}\
    Merit-based scholarship.\\
    
    \ressubheading{AP Scholar Award}{}{J.P. Taravella High}{Apr. 2006}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Activism}

        \begin{description}\setlength{\itemsep}{0mm}
        \item[2015] Helped organize a Surveillance Self-Defence for Activists Workshop.
        \item[2014 $\rightarrow$ Present] Part of the \#BlackLivesMatter movement.
        \item[2012] Full-time land-based spotting, tracking, mapping, and data entry of humpback whale behaviour (\hyperlink{whalevolunteering}{description} above).
        \item[2008] Full-time volunteer for Common Ground Relief, a non-profit organization providing relief in New Orleans following the Hurricane Katrina disaster. Helped reclaim wetlands, established a community garden, and build a house with Americorps.
        \item[2006 $\rightarrow$ Present] I am passionate about the open source philosophy and free culture. I contribute to Wikipedia Commons, Linux, and BOINC amongst others.
        \item[2006 $\rightarrow$ 2007] Part-time volunteer for North Ridge Medical Center in Oakland Park, FL.  Transported patients, manned the front desk, routed calls, and customer support.
        \end{description}


\end{document}


% FUTURE SECTIONS//GRAVEYARD


%Trainees
%Editorial Responsibilities
%Patents

%%-------Coursework
%\section{Relevant Coursework}
%\vspace{-20pt} %space fix
%\begin{multicols}{2}
%\begin{my_itemize}
%\item Biochemistry I \& II with Lab
%\item Genetics with Lab
%%\item Classical Genetics Techniques Laboratory
%%     \item Fundamentals of Applied Genetics
%\item Cell Biology with Lab
%\item Organic Chemistry I \& II with Labs
%\item Inorganic \& Bioinorganic Chemistry
%\item Thermodynamics of Biomolecular Systems %\& Lab
%\item Organismic Biology
%\item Ordinary Differential Equations
%\item Calculus with Theory % \& ODE
%\end{my_itemize}
%\end{multicols}
%\vspace{-12pt}%space fix